---
title: "Homework6"
author: "Xinyao Wu"
date: "2018/11/16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(broom)
```

##problem1

*tidy data
```{r}
wp_df = read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  #Create a city_state variable and a binary variable indicating whether the homicide is solved.
  mutate(
    city_state = str_c(city,state,","), 
    solve = ifelse(disposition == "Closed by arrest",TRUE,FALSE)
  )


```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.





##problem2




