---
title: "Homework6"
author: "Xinyao Wu"
date: "2018/11/16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(broom)

```

##problem1

__Washington Post__


####Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.

```{r}
Original_data = read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
wp_df = 
  Original_data %>% 
  janitor::clean_names() %>% 
  #Create a city_state variable and a binary variable indicating whether the homicide is solved.
  mutate(
    city_state = str_c(city,state, sep = ", "), 
    resolved = as.numeric(disposition == "Closed by arrest")
  ) %>% 
  #Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO
  filter(
    city_state != "Dallas, TX" & city_state !="Phoenix, AZ" & city_state !="Kansas City, MO" & city_state !="Tulsa, AL"
  ) %>% 
  mutate(
    victim_race = ifelse(victim_race =="White","white","non_white"),
    victim_race = fct_relevel(victim_race, "white"),
    victim_age = as.numeric(victim_age)
  )
wp_df %>% head(5) 

```


####For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
__Save the output of glm as an R object; __
apply the  broom::tidy to this object; 
and __obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.__

```{r}
#For the city of Baltimore, MD
baltimore = wp_df %>% 
  filter(city_state =="Baltimore, MD") 
#fit a logistic regression
fit_baltimore = glm(resolved ~ victim_age + victim_sex + victim_race , family = binomial(), data = baltimore)

broom::tidy(fit_baltimore)
#the estimate of the adjusted odds ratio for solving homicides comparing non-white victims to white victims
coef(fit_baltimore)["victim_racenon_white"] %>% exp()
#the confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims
confint(fit_baltimore,"victim_racenon_white")%>% exp()
```

####Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims.
Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r warning=FALSE}
 city_glm =
  wp_df %>% 
  select(resolved, city_state, victim_race,victim_age,victim_sex) %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(
    model = map(data,~glm(resolved ~ victim_age + victim_sex + victim_race ,family = binomial(),data = .)),
    model = map(model, ~broom::tidy(.,conf.int = TRUE))
)  %>% 
   select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon_white")  %>% 
  mutate(OR = exp(estimate),
         CI.low = exp(conf.low),
         CI.high = exp(conf.high)) %>% 
  select(city_state,OR,CI.low ,CI.high ) 

city_glm
```

####Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
city_glm %>% 
  mutate(
    city_state = reorder(city_state,desc(OR))
  ) %>% 
ggplot(aes(x = city_state, y = OR))+ geom_line()+
  geom_errorbar(aes(x= city_state,ymin = CI.low, ymax = CI.high))+
  labs(
    y = "Odd ratio ",
    title = "odd ratio of homocides solving comparing non-white to white victims in United States"
  )+
  theme(
    axis.text.x = element_text(angle = 90 , hjust = 1)
  )
  
```




##problem2




